--- 
title: "A Minimal Book Example"
author: "Sergio"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: https://github.com/sergiogoro/minimal-bookdown-sergio
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

- Download and install R:  
    - https://cran.r-project.org/  

- Downoad and install RStudio:  
    - https://www.rstudio.com/products/rstudio/download/  
    - Configure RStudio:  
    - ...  

- Install R packages (from RStudio for example):  
    - Bookdown (development version on GitHub):  

```{r eval=FALSE}
devtools::install_github("rstudio/bookdown")
```
    - Tinytex:  
        - To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.  
````{r eval=FALSE}
devtools::install_github(c('yihui/tinytex', 'rstudio/rmarkdown'))
tinytex::install_tinytex()
````


```{r include=FALSE}  
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

    <!---
    [//]: # Knitr:  
        - install.packages('knitr', dependencies = TRUE)  
    --->

# How to minimal Bookdown
- Download the [minimal-bookdown-sergio](https://github.com/sergiogoro/minimal-bookdown-sergio) GitHub repository as a [Zip](https://github.com/sergiogoro/minimal-bookdown-sergio/archive/master.zip) file, then unzip it locally.  
- 

- 
- 
